---
output: github_document
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# hmmibdr

Direct wrapper for [HMMIBD](https://github.com/glipsnort/hmmIBD) in Rcpp. 

## Installation

You can install the latest version using:

```{r gh_installation, message=FALSE, eval = FALSE}
#install.packages("devtools")
devtools::install_github("OJWatson/hmmibdr")
```

```{r}
# Load the package
library(hmmibdr)
```

## Demonstration

Firstly, with one population:

```{r sc}
## one population
tf <- tempfile(pattern = "output_Cambodia")
out <- hmm_ibd(input_file = system.file("extdata/pf3k_Cambodia_13.txt", package = "hmmibdr"),
               allele_freqs =  system.file("extdata/freqs_pf3k_Cambodia_13.txt", package = "hmmibdr"),
               output_file = tf)
```

`hmmibdr` now returns the relevant fractions and segments as a list. Firstly the fraction of sites IBD:

```{r list returns}
head(out$fract)
```

And the segments compared:

```{r list segments}
head(out$segments)
```

`hmmibdr` also can be run for two populations:

```{r surv}
## two pops
tf2 <- tempfile("output_Cambodia_Ghana")
out <- hmm_ibd(input_file = system.file("extdata/pf3k_Cambodia_13.txt", package = "hmmibdr"),
               allele_freqs = system.file("extdata/freqs_pf3k_Cambodia_13.txt", package = "hmmibdr"),
               genotypes_sec_pop = system.file("extdata/pf3k_Ghana_13.txt", package = "hmmibdr"),
               allele_freqs_sec_pop = system.file("extdata/freqs_pf3k_Ghana_13.txt", package = "hmmibdr"),
               output_file = tf2)
